Enforced Invariant Confluence

### 2018-05-01 doc/paper/sections/related_work.tex
Integrating Joe's feedback.
Added section on Calvin, Janus, TAPIR.

@@

\textbf{CALM Theorem.}
Bloom~\cite{alvaro2010boom, alvaro2011consistency, conway2012logic} and its
formalism, Dedalus~\cite{alvaro2011dedalus, alvaro2013declarative}, are
declarative Datalog-based programming languages that are designed to program
distributed systems. The accompanying CALM
theorem~\cite{hellerstein2010declarative, ameloot2013relational} states that if and only if
a program can be written in the monotone fragment of these languages, then
there exists a consistent, coordination-free implementation of the program.  The CALM
theorem provides guarantees about the consistency of program outputs. It does not directly capture our notions of transactions or invariance maintenance during program execution.
Moreover, Bloom and Dedalus are general purpose programming
languages that can be used to implement a variety of distributed systems that
are outside of the scope of \invariantconfluence{}.

% \textbf{Program Analysis in Database Systems.}
% Using program analysis to improve the performance of database systems is not
% new. For example, it has been used to improve the performance of
% database-backed web applications~\cite{cheung2014using, wu2016transaction,
% ramachandra2012program} and used to improve the performance of optimistic
% concurrency control on multi-core machines~\cite{wu2016transaction}. Our work
% on \invariantconfluence{} continues the theme of using program analysis to reap
% the performance benefits gained from understanding program semantics.

>>>>

\textbf{Serializable Distributed Databases.}
In \secref{Evaluation}, we saw that segmented \invariantconfluent{} replication
vastly outperforms linearizable replication for low coordination workloads, and
it performs comparably or worse for medium and high coordination workloads.
Distributed databases like Calvin~\cite{thomson2012calvin},
Janus~\cite{mu2016consolidating}, and TAPIR~\cite{zhang2015building} employ
algorithmic optimizations to implement serializable transactions with high
throughput and low latency.
%
While segmented \invariantconfluent{} replication will likely always outperform
serializable replication for low coordination workloads, these databases make
serializable replication the most performant option for executing workloads
that require a modest amount of coordination.

@@

\textbf{CALM Theorem.}
Bloom~\cite{alvaro2010boom, alvaro2011consistency, conway2012logic} and its
formalism, Dedalus~\cite{alvaro2011dedalus, alvaro2013declarative}, are
declarative Datalog-based programming languages that are designed to program
distributed systems. The accompanying CALM
theorem~\cite{hellerstein2010declarative, ameloot2013relational} states that if
and only if a program can be written in the monotone fragment of these
languages, then there exists a consistent, coordination-free implementation of
the program.  The CALM theorem provides guarantees about the consistency of
program outputs. It does not directly capture our notions of transactions or
invariant maintenance during program execution.  Moreover, Bloom and Dedalus
are general purpose programming languages that can be used to implement a
variety of distributed systems that are outside of the scope of
\invariantconfluence{}.

\textbf{Program Analysis in Database Systems.}
Using program analysis to improve the performance of database systems is not
new. For example, it has been used to improve the performance of
database-backed web applications~\cite{cheung2014using, wu2016transaction,
ramachandra2012program} and used to improve the performance of optimistic
concurrency control on multi-core machines~\cite{wu2016transaction}. Our work
on \invariantconfluence{} continues the theme of using program analysis to reap
the performance benefits gained from understanding program semantics.
